---
title: "Flow Charts for Manuscript"
output: html_document
date: "2023-02-07"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(DiagrammeR)
library(tidyverse)
```

# Intro to SEM

## Imagine we have four variables and we want to study thier indirect and direct interactions

```{r Basic, echo=FALSE}
# Four standalone nodes

grViz("
  digraph flowchart {
    node [shape=circle, fontsize=14, color=lightblue, style=filled]
    a
    b
    c
    d
  }
")
```

## Linear models (Multiple regression)

```{r GLM, echo=FALSE}
# Linear models (Multiple regression)

grViz("
  digraph flowchart {
    node [shape=circle, fontsize=14, color=lightblue, style=filled]
    a -> d
    b -> d
    c -> d
  }
")
```

## Multivariate models (MANOVA)

```{r MANOVA, echo=FALSE}
# Linear models (Multiple regression)

grViz("
  digraph flowchart {
    node [shape=circle, fontsize=14, color=lightblue, style=filled]
    a -> d
    b -> d
    c -> d
  }
")
```

# SEMs utility as an extension of GLM and MANOVA

## Indirect effects mean a node can be both a predictor and a response variable. Here A indirectly affects B via D


```{r SEM1, echo=FALSE}
grViz("
  digraph flowchart {
    node [shape=circle, fontsize=14, color=lightblue, style=filled]
    a -> c
    a -> d
    d -> b
    {rank=same; a b}
    a -> b [color=red, penwidth=1, style=solid, arrowhead=normal]
  }
")
```

# Chains of serial direct effects
## A Both directly and indirectly affects C and D through multiplying path coefficients


```{r SEM2, echo=FALSE}
grViz("
  digraph flowchart {
    node [shape=circle, fontsize=14, color=lightblue, style=filled]
    a -> b
    b -> c
    c -> d
    {rank=same; a b c d}
    a -> c [color=black, penwidth=1, style=dotted, arrowhead=normal]
    a -> d [color=black, penwidth=1, style=dotted, arrowhead=normal]
  }
")
```

# Limitations of SEM
## SEM cannot resolve networks with cyclical parts

```{r SEM3, echo=FALSE}
grViz("
  digraph flowchart {
    node [shape=circle, fontsize=14, color=lightblue, style=filled]
    a -> b
    b -> c
    c -> a 
    c -> d
    {rank=same; b c}
  }
")
```

## Reciprocal or bidirectional paths cause the same issue as cyclical diagrams

```{r SEM4, echo=FALSE}
 grViz("
  digraph flowchart {
    node [shape=circle, fontsize=14, color=lightblue, style=filled]
    a -> b
    b -> a
    a -> c 
    b -> d
    {rank=same; a b}
  }
") 
```