---
title: "Literature Review"
output: 
  html_document:
    css: "Water.css"
date: "2023-01-16"
author: "Robert Clark, Emily Rampone, Robert Orpet, & David Crowder"
---

```{css, echo=FALSE}
pre {
  max-height: 200px;
  overflow-y: auto;
}

pre[class] {
  max-height: 100px;
}
```

# Score-counting literature review

These data are a list of publications using path analysis or SEM in applied entomology. These include agricultural systems, forest natural resources, or other integrated pest management projects. 

<blockquote>
Web of Science search terms included "insect*" AND "pest", "“path analysis” OR "structural equation model", but excluded results for SEM involving scanning electron microscopy.



```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
library(readxl)
library(kableExtra)
library(gridExtra)

# Additional packages or installs
# library(DT)
# webshot::install_phantomjs()

```

# Data availability

<fieldset>
[Data is available to our github repository.](https://github.com/robclark19/pathanalysismethods/tree/main/References)

# Upload spreadsheet
```{r data, echo = T, results = 'hide'}

lit_data <- readxl::read_xlsx("./References/SEM SLR.xlsx", sheet = "Current") %>% 
  as.data.frame() %>% 
  select(-c(Paper, Journal)) %>% # drop long text columns
  rename(type = Tag2_Type, system = Tag1_Systems, topic = Tag3_Interaction)
  
```

# Literature summary data

Literature survey data includes authors, dates, then categorizes based on study system, broad research categories, and the types of ecological interactions being evaluated.

```{r table, echo = FALSE}

lit_data %>% 
  head() %>%
  kable()
  
```


## Score-counting bar chart

Score counting chart

```{r scores, echo=FALSE}

# count the number of entries across the dataset for each category
type_counts <- lit_data %>% count(type)
system_counts <- lit_data %>% count(system)
topic_counts <- lit_data %>% count(topic)


# create the bar plot for type counts
bar_plot <- function(data, x_var, y_var){
  ggplot(data, aes(x = x_var, y = y_var)) +
    geom_bar(stat = "identity") +
    ylab("Count") +
    xlab("")
}

# make three plots
type_plot <- bar_plot(type_counts, type_counts$type, type_counts$n)
system_plot <- bar_plot(system_counts, system_counts$system, system_counts$n)
topic_plot <- bar_plot(topic_counts, topic_counts$topic, topic_counts$n)

# to stitch together multiple ggplot objects
grid.arrange(type_plot, system_plot, topic_plot, nrow=3)




```

