---
title: "Literature Review"
output: 
  html_document:
    css: "Water.css"
date: "2023-01-16"
---

# Score-counting literature review

These data are a list of publications using path analysis or SEM in applied entomology. These include agricultural systems, forest natural resources, or other integrated pest management projects. 

Search phrases used in Web of Science include "insect*" AND "pest", "“path analysis” OR "structural equation model". See metadata in ![Meta tab](https://github.com/robclark19/pathanalysismethods/blob/main/References/SEM%20SLR.xlsx).


```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
library(readxl)

```

## Import data

```{r data, echo = True, results = 'hide'}

lit_data <- readxl::read_xlsx("./References/SEM SLR.xlsx", sheet = "Current") %>% 
  as.data.frame() %>% 
  select(-c(Paper, Journal)) # drop long text columns
  
```

## Manipulate data for a side-by-side comparison

```{r table, echo = True}


  
```


## Score-counting bar chart

```{r scores, echo=FALSE}


head(lit_data)

```

